A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit result 4

        \item For the \mtot{} matched sample, although there is a clear and robust 
            difference between the two median \mden{} profiles, the overall difference 
            is subtle is mainly only apparent on $R>50$ kpc scales. 
            The logarithmic scale of \mden{} on the Y-axis is partially responsible 
            for the subtle differences we see here.  
            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same
            comparison using the curve--of--growth of \mstar{} and the fraction of 
            \mtot{} enclosed in elliptical apertures with different radius. 
            Both of the illustrate the same results from slightly different angles.

@@

%This may explain why previous attempts to detect this signal using 
            %shallower images were not successful.

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
    contrast with the large \textit{intrinsic} scatter in the outskirts. 
    It hints that these two regions are shaped by distinctive processes, and may 
    explain why they depend on environment at different levels.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The scatter of halo assembly process at fixed halo mass and the stochastic 
    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
    scatter in the outer \mden{} profiles and the diversity seen on the 
    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

@@

    \todo{Move to discussion}
    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
    \mden{} in the central region than their descendants, hence it is necessary to 
    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
    profiles of massive central galaxies at low-$z$.
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.
%% ------------------------------------------------------------------------------------ %%

@@

    Results presented here are broadly consistent with the ``two-phase'' formation
    scenario of massive central galaxies in a hierarchical universe. 
    Under this picture, intense dissipative processes at $z > 2$ are responsible for 
    the formation of the \textit{in situ} stars in massive central galaxies. 
    After the star formation was quenched, the more gradual second phase of evolution
    is dominated by non-dissipative mergers of satellite galaxies. 
    Since dry minor mergers can effectively deposit \textit{ex situ} stars on to the 
    outskirts of these massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), 
    it is expected that the stellar mass distributions of massive galaxies 
    show halo mass dependence, as the central galaxies of more massive haloes should
    experience more mergers.

    \citet{Shankar2014} investigates the environment dependence of galaxy size using 
    a series of hierarchical semi-analytic models. 
    All models suggest that, at fixed stellar mass, the median size of galaxies 
    strongly increases with halo mass. 
    Although the centrals of more massive halos only experience slightly higher 
    number of major mergers (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013}), 
    the number of minor mergers strongly depend on the assumed dynamical friction time. 
    If short dynamical friction time is favored (e.g. \citealt{Newman2012}), 
    centrals of more massive haloes can have up to four times more minor mergers 
    (1:100--1:3). 
    These extra minor mergers alone can lead to moderate halo mass dependence of 
    size. 
    Similarly, \citet{Yoon2017} confirms these theoretical predictions using 
    semi-analytic model from \citet{Guo2011}.

@@

    More importantly, our results show that the inner region of massive central 
    galaxies also play a role here. 
    Both the \mden{} profiles of \mtot{}--matched samples and the \mtot{}--\minn{}
    plane suggest that, at fixed \mtot{}, centrals of more massive haloes have 
    slightly shallower inner \mden{} slope and lower \mtot{}.  
    Minor mergers can not explain such difference as they should not alter the inner 
    \mden{} profiles. 
    This is also not caused by the choice of outer aperture to estimate ``total''
    \mstar{}: assuming that centrals in more massive haloes have more extended 
    \mden{} profiles, integration out to larger aperture will make the differences 
    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more significant. 
    The fact that, at fixed \mtot{}, the overall stellar mass distributions of massive
    central galaxies relate to halo mass may hint us more insights about the connection 
    between the assembly of massive haloes and their central galaxies, and it is worth 
    further investigation.

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering 
    \includegraphics[width=16cm]{fig/redbcg_match}
    \caption{
        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
        corresponding to the results shown in the left figure of   
        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
        whose size reflects the $P_{\mathrm{Cen}}$ value.  
        We also color-code them using the richness ($\lambda$) of the host cluster. 
        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
        To further evaluate the matching results, we show the distributions of \mtot{} 
        (middle panel) and redshift (bottom panel) separately. 
        On both panesl, we show the histograms along with their kernel density 
        distributions.  
        And, on the top of each panel, two sets of short vertical lines highlight the median 
        value (solid) and the inter-quartile (dash) of each distribution.~~~
        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
        samples used for the right figure of Fig~\ref{fig:prof_1}.
        The format is exactly the same as the left one, except the \minn{} replaces the 
        \mtot{} in the top and middle panels.}
    \label{fig:match}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
	\label{app:cog}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/redbcg_prof_m100D}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.
        }
    \label{fig:cog}
\end{figure}
%% ------------------------------------------------------------------------------------ %%

>>>>

        \item For the \mtot{} matched sample, although there is a clear and robust 
            difference between the two median \mden{} profiles, the overall difference 
            is quite subtle, especially in the inner region. 
            The difference becomes more apparent at $R>50$ kpc scales.

@@

    The logarithmic scale of \mden{} on the Y-axis is partially responsible for the 
    subtle differences we see in the fixed \mtot{} comparison.  
    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same 
    comparison using the curve--of--growth of \mstar{} and the fraction of \mtot{} 
    enclosed in elliptical apertures with different radius. 
    Both of the illustrate the same results from slightly different angles. 
    They also both suggest that, at fixed \mtot{}, the environmental dependence of 
    \mden{} profiles is indeed quite subtle. 
    This may explain why previous attempts to detect such dependence using shallower 
    images often failed. 
    More importantly, this result also suggests that halo mass does not play the 
    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
    stellar mass}.

    It is therefore interesting to see the comparison of \mden{} profiles at fixed 
    \minn{}--a reasonable tracer for the stellar mass in the \textit{in situ}
    component (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo. 
    Also, the similar slopes of the \mden{} profiles within 10 kpc are in sharp 
    contrast with the large \textit{intrinsic} scatter we see in the outer \mden{} 
    profiles. 
    This hints that these two regions could be shaped by distinctive physical 
    processes, and may explain why they depend on halo mass differently.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The scatter of halo assembly histories at fixed halo mass and the stochastic 
    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
    scatter in the outer \mden{} profiles and the diversity seen on the 
    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

@@

@@

    Results presented here are broadly consistent with the ``two-phase'' formation
    scenario for massive central galaxies in a hierarchical universe. 
    Under this picture, intense dissipative processes at $z > 2$ are responsible for 
    the formation of the \textit{in situ} stars in massive central galaxies. 
    After the star formation was quenched, a more gradual second phase is dominated 
    by non-dissipative mergers of satellite galaxies. 
    Since dry minor mergers can effectively deposit \textit{ex situ} stars in the 
    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), 
    it is expected that the stellar mass distributions of massive galaxies 
    show halo mass dependence, as the central galaxies of more massive haloes should
    experience more mergers.

    \citet{Shankar2014} investigates the environment dependence of galaxy size using 
    a series of hierarchical semi-analytic models. 
    All models suggest that, at fixed stellar mass, the median size of galaxies 
    strongly increases with halo mass. 
    Although the centrals of more massive halos only experience slightly higher 
    number of major mergers (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013}), 
    the number of minor mergers strongly depend on the assumed dynamical friction time. 
    When short dynamical friction time is favored (e.g. \citealt{Newman2012}), 
    centrals of more massive haloes can have up to four times more minor mergers 
    (1:100--1:3). 
    These extra minor mergers alone can lead to moderate halo mass dependence of 
    galaxy size. 
    Similarly, \citet{Yoon2017} confirms these theoretical predictions using 
    semi-analytic model from \citet{Guo2011}.

@@

    More importantly, our results show that the inner region of massive central 
    galaxies also play a role here. 
    Both the \mden{} profiles of \mtot{}--matched samples and the \mtot{}--\minn{}
    plane suggest that, at fixed \mtot{}, centrals of more massive haloes have 
    slightly shallower inner \mden{} slope and lower fraction of \mtot{} within the 
    inner 10 kpc.
    Minor mergers can not explain such difference as they should not alter the inner 
    \mden{} profiles. 
    This is also not caused by the choice of outer aperture to estimate ``total''
    \mstar{}: assuming that centrals in more massive haloes have more extended 
    \mden{} profiles, integration out to larger aperture will make the differences 
    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more 
    significant.

    Observations of compact quiescent galaxies at high-$z$ seem to indicate higher 
    \mden{} in their central regions than their descendants. 
    Therefore it is necessary to rely on certain processes to reduce the central 
    \mden{} (e.g. strong adiabatic expansion induced by powerful AGN feedback; 
    \citealt{Fan2008}) to match the inner \mden{} profiles of massive central galaxies 
    at lower redshift.
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which 
    is common in the assembly history of massive galaxies, can also flatten the 
    central \mden{} profile via efficient scattering effect 
    (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
    by problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large 
    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
    Bonfini2016}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering 
    \includegraphics[width=15.0cm]{fig/redbcg_match}
    \caption{
        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
        corresponding to the results shown in the left figure of   
        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
        whose size reflects the $P_{\mathrm{Cen}}$ value.  
        We also color-code them using the richness ($\lambda$) of the host cluster. 
        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
        To further evaluate the matching results, we show the distributions of \mtot{} 
        (middle panel) and redshift (bottom panel) separately. 
        On both panesl, we show the histograms along with their kernel density 
        distributions.  
        And, on the top of each panel, two sets of short vertical lines highlight the median 
        value (solid) and the inter-quartile (dash) of each distribution.~~~
        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
        samples used for the right figure of Fig~\ref{fig:prof_1}.
        The format is exactly the same as the left one, except the \minn{} replaces the 
        \mtot{} in the top and middle panels.}
    \label{fig:match}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
	\label{app:cog}

	In \S \ref{ssec:sbp_mtot} and Figure \ref{fig:prof_1}, we show the comparisons 
	of \mden{} profiles for massive central galaxies from the \rbcg{} and \nbcg{} 
	samples. 
	Although the differences in their median \mden{} profiles we revealed are robust 
	and systematic, they appear to be very subtle, especially in the inner region. 
	This is partly due to the logarithmic scale on the Y--axis for \mden{} profiles.

	In Figure \ref{fig:cog}, we compare the same two samples after converting the 
	\mden{} profiles into:

	    \item ``Curve--of--growth'' of stellar mass--the cumulative \logms{} profiles
	        (upper panel).

	    \item Fraction of \mtot{} within different radius (lower panel).

	These comparisons demonstrate the same results from different angles and 
	the systematic differences become more clear using the fraction of \mtot{}
	within different radius.  
	The comparison of cumulative \logms{} profiles also demonstrates that the 
	\rbcg{} and \nbcg{} samples have very similar median \mtot{}.  
    They help confirm that the distributions of stellar mass within 100 kpc indeed 
    have systematic differences between the massive central galaxies living in more 
    and less massive dark matter haloes.

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/redbcg_prof_m100D}
    \caption{
        \textbf{Top:} comparison of the cumulative \mstar{} profiles for 
        \rbcg{} (orange--red) and \nbcg{} (grey--black) galaxies at fixed \mtot{}.~~
        \textbf{Bottom:} comparison of the fraction of \mtot{} within different radius 
        for the same samples at fixed \mtot{}. 
        Thicker and darker solid lines highlight the median profiles. 
        Other formats of the figure are similar to Figure \ref{fig:prof_1}. 
        Besides the region affected by seeing, the 10 and 100 kpc radius, we 
        also highlight the 50\% and 100\% values using horizontal grey lines on the 
        bottom panel. 
        }
    \label{fig:cog}
\end{figure}
%% ------------------------------------------------------------------------------------ %%
